Applications of limited information strategies in Menger's game

### 2015-08-25 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
edited through end of 3rd section

@@

\keywords{Menger's property, Menger's game, limited information strategies}
% \begin{keyword}
%   Proximal\sep absolutely proximal\sep Corson compact\sep uniform space\sep \(W\)-space
% \end{keyword}

@@

It can be shown via a non-trivial
proof that the following game can be used to characterize the Menger property.

\begin{definition}
  For each cover \(\mc U\) of \(X\), \(S\subseteq X\) is \term{\(\mc U\)-finite} if
  there exists a finite subcollection of \(\mc U\) which covers \(C\).
\end{definition}

@@

@@

\begin{theorem}
  A space \(X\) is Menger if and only if \(\pl C\notwin\menGame{X}\)
  \cite{MR1544773}.
\end{theorem}

The typical characterization of the Menger game involves \(\pl F\) choosing
a finite subcollection \(\mc F_n\) of \(\mc U_n\), but it is easy to see that the
characterization given above is equivalent, and will be convenient for use
in our proofs.

\section{Markov strategies}

To the author's knowledge, no other direct work has been done on limited
information strategies pertaining to the Menger game, although as we'll see
there are results which can be sharpened when considering them.
However, we immediately see that tactics are not of any real interest.

\begin{proposition}
  \(X\) is compact if and only if
  \(\pl F \tactwin \menGame{X}\) if and only if
  \(\pl F \ktactwin{k} \menGame{X}\).
\end{proposition}

\begin{proof}
  If \(\sigma\) is a winning \(k\)-tactic, then for each open cover \(\mc U\),
  \(\sigma\) defeats the attack \(\<\mc U,\mc U,\dots\>\). Then
  \[
    \bigcup_{i\leq k} \sigma(\<\underbrace{\mc U,\dots,\mc U}_i\>) = X
  \]
  and \(X\) is \(\mc U\)-finite.
\end{proof}

@@

\begin{theorem}
  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\).
\end{theorem}

\begin{proof}
  This result will later follow from the fact that
  \(\oneptlind\omega_1\) is not a \(\sigma\)-compact space (all its compact subsets
  are finite).

  For now, let \(\sigma\) be a Markov strategy for \(\pl F\). For
  each \(\alpha<\omega_1\), let \(\mc U_\alpha\) be the open cover
  \(\{\{\beta\}:\beta<\alpha\}\cup\{\oneptlind{\omega_1}\setminus\alpha\}\) of
  \(\oneptlind{\omega_1}\), and set \(F(\alpha,n)\) to be the finite set
  \(\alpha\cap\sigma(\<\mc U_\alpha\>,n)\).

  If
    \(
      P_n =
      \{\beta: \beta < \alpha < \omega_1 \Rightarrow \beta \in F(\alpha,n)\}
    \),
  then \(P_n\subseteq F(\sup(P_n)+1,n)\). Thus \(P_n\) is finite for \(n<\omega\).
  Choose \(\beta\in\omega_1\setminus \bigcup_{n<\omega}P_n\)
  and \(\alpha_n>\beta\) such that \(\beta\not\in F(\alpha_n,n)\).
  Then \(\pl C\) may attack
  \(\sigma\) with \(\<\mc U_{\alpha_0}, \mc U_{\alpha_1},\dots\>\),
  and it follows that
  \(\beta\not\in \bigcup_{n<\omega}F(\alpha_n,n)\) and
  \(\beta\not\in \bigcup_{n<\omega}\sigma(\<\mc U_{\alpha_n}\>,n)\).
\end{proof}

The greatest advantage of a strategy which has knowledge of two or more previous
moves of the opponent, versus only knowledge of the most recent move, is the
ability to react to changes from one round to the next. It's this ability to
react that will give \(\pl F\) her winning \(2\)-Markov strategy in the Menger
game on \(\oneptlind\omega_1\).

For inspiration, we turn to a game whose \(n\)-tactics were studied by Marion
Scheepers in \cite{MR1129143} which has similar goals to the Menger game when
played upon \(\oneptlind\kappa\).

\begin{game}
  Let \(\cloFillStrictGame\kappa\) denote the \term{strict union filling game}
  with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
  \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
  \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
  by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).

@@

In \(\menGame{\oneptlind\kappa}\), \(\pl C\) essentially chooses a countable set
to not include in her neighborhood of \(\infty\), followed by \(\pl F\) choosing
a finite subset of this complement to cover during each round. Thus,
\(\pl F\) need only be concerned with the \textit{intersection} of the
countable sets chosen by \(\pl C\) in \(\menGame{\oneptlind\kappa}\), rather
than the union as in \(\cloFillStrictGame\kappa\).

Another difference: Scheepers required that \(\pl C\) always choose strictly
growing countable sets. The reasoning is clear: if the goal is to study tactics,
then \(\pl C\) cannot be allowed to trap \(\pl F\) in a loop by repeating the same
moves. But by eliminating this requirement, the study can then turn to Markov
strategies, bringing the game further in line with the Menger game played upon
\(\oneptlind\kappa\).

We introduce a few games to make the relationship between Scheeper's
\(\cloFillStrictGame\kappa\) and \(\menGame{\oneptlind\kappa}\) more precise.

\begin{game}
  Let \(\cloFillGame\kappa\) denote the
  \term{union filling game} which proceeds analogously
  to \(\cloFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
  is reduced to \(C_{n+1}\supseteq C_n\).
\end{game}

\begin{game}
  Let \(\cloFillInitialGame\kappa\) denote the
  \term{initial filling game} which proceeds analogously
  to \(\cloFillGame\kappa\), except that \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq C_0\).
\end{game}

\begin{game}
  Let \(\cloFillIntGame\kappa\) denote the
  \term{intersection filling game} which proceeds analogously
  to \(\cloFillInitialGame\kappa\), except that \(\pl C\) may choose any
  \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n\).
\end{game}

\begin{figure}[h]
\begin{center}
% \begin{tikzpicture}
%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
%   {
%     \pl F \kmarkwin{k}\menGame{\oneptlind\kappa} &
%     \pl F \kmarkwin{k}\cloFillIntGame\kappa \\

%     \pl F \kmarkwin{k}\cloFillInitialGame\kappa &
%     \pl F \kmarkwin{k}\cloFillGame\kappa \\

%     &
%     \pl F \ktactwin{k}\cloFillStrictGame\kappa \\
%   };
%   \path[>=latex,->]
%     (m-1-1) edge (m-2-1)
%     (m-1-2) edge (m-2-2)
%     (m-3-2) edge (m-2-2);
%   \path[>=latex,<->]
%     (m-1-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2);
% \end{tikzpicture}
\end{center}
\caption{Diagram of Filling/Menger game implications}
\label{fillingGamesDiagram}
\end{figure}

\begin{theorem}
For any cardinal \(\kappa>\omega\) and integer \(k<\omega\),
Figure \ref{fillingGamesDiagram} holds.
\end{theorem}

\begin{proof}
  \(\pl F \kmarkwin{k}\menGame{\oneptlind\kappa}
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillIntGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\menGame{\oneptlind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
  countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
  into the open cover \([C]^1\cup\{\oneptlind\kappa\setminus C\}\)
  (resp. finite sequence of such open covers). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      C\cap\sigma(\mc U(s\concat\<C\>),n)
    \]
  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillIntGame\kappa\).

  \(\pl F \kmarkwin{k}\cloFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\menGame{\oneptlind\kappa}\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\cloFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
  cover \(\mc U\) of \(\oneptlind\kappa\) (resp. finite sequence \(s\) of such covers)
  into a countable set \(C\) which is the complement of some neighborhood of
  \(\infty\) in \(\mc U\) (resp. finite sequence of such countable sets).
  Then \(\tau\) defined by
    \[
      \tau(s\concat\<\mc U\>,n)
        =
      (\oneptlind\kappa\setminus C(\mc U))
        \cup
      \sigma(C(s\concat\<\mc U)\>),n)
    \]
  is a winning \(k\)-mark for \(\pl F\) in \(\menGame{\oneptlind\kappa}\).

  \(\pl F \kmarkwin{k}\cloFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\cloFillIntGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
  in \(\cloFillInitialGame\kappa\).

  \(\pl F \kmarkwin{k}\cloFillInitialGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillGame\kappa\): Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\cloFillInitialGame\kappa\). For each finite sequence \(s\), let \(t\preceq s\) mean \(t\)
  is a final subsequence of \(s\). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      \bigcup_{t\preceq s, m\leq n}
      \sigma(t\concat\<C\>,m)
    \]
  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillGame\kappa\).

  \(\pl F \kmarkwin{k}\cloFillGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\cloFillGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
  in \(\cloFillInitialGame\kappa\).

  \(\pl F \ktactwin{k}\cloFillStrictGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-tactic for \(\pl F\) in
  \(\cloFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
  be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
  Then \(\tau\) defined by
    \[
      \tau(\<C_0,\dots,C_i\>,n)
        =
      \sigma(\<C_0+(n-i),\dots,C_i+n\>)
    \]
  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillGame\kappa\).
\end{proof}

While we have not proven a direct implication between the Menger game and
Scheeper's original filling game, Scheepers introduced the statement
\(\alcompS\kappa\) relating to the almost-compatability of functions
from countable subsets of \(\kappa\) into \(\omega\) which may be applied to
both.

@@

Scheepers went on to show that \(\alcompS\kappa\) implies
\(\pl F \ktactwin2 \cloFillStrictGame\kappa\). This proof, along with the following
facts, give us inspiration for
finding a winning \(2\)-Markov strategy in the Menger game played on
\(\oneptlind\kappa\).

@@

\begin{figure}[h]
\begin{center}
% \begin{tikzpicture}
%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
%   {
%     &
%     \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
%     \pl F \kmarkwin2\cloFillIntGame\kappa \\

%     \alcompS\kappa &
%     \pl F \kmarkwin2\cloFillInitialGame\kappa &
%     \pl F \kmarkwin2\cloFillGame\kappa \\

%     &
%     &
%     \pl F \ktactwin2\cloFillStrictGame\kappa \\
%   };
%   \path[>=latex,->]
%     (m-2-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2)
%     (m-2-1) edge (m-3-3)
%     (m-1-2) edge (m-2-2)
%     (m-1-3) edge (m-2-3)
%     (m-3-3) edge (m-2-3);
%   \path[>=latex,<->]
%     (m-1-2) edge (m-1-3)
%     (m-2-2) edge (m-2-3);
% \end{tikzpicture}
\end{center}
\caption{Diagram of Filling/Menger game implications with \(\alcompS\kappa\)}
\label{fillingGamesDiagram2}
\end{figure}

@@

\begin{proof}
  Since \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\cloFillStrictGame\kappa\) was
  a main result of \cite{MR1129143}, it is sufficient to show that
  \(\alcompS\kappa\Rightarrow \pl F \kmarkwin2\cloFillIntGame\kappa\).

@@

\begin{figure}[h]
\begin{center}
% \begin{tikzpicture}
%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
%   {
%      \pl F \markwin \menGame{X} &
%      \pl F \kmarkwin2 \menGame{X} &
%      \pl F \win \menGame{X} &
%      \pl C \notwin \menGame{X} \\

%      \text{Markov Menger} &
%      2\text{-Markov Menger} &
%      \text{Perfect Menger} &
%      \text{Menger} \\
%   };
%   \path[>=latex,<->]
%     (m-1-1) edge (m-2-1)
%     (m-1-2) edge (m-2-2)
%     (m-1-3) edge (m-2-3)
%     (m-1-4) edge (m-2-4);
%   \path[>=latex,->]
%     (m-1-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2)
%     (m-1-2) edge (m-1-3)
%     (m-2-2) edge (m-2-3)
%     (m-1-3) edge (m-1-4)
%     (m-2-3) edge (m-2-4);
%   \path[>=latex,->,bend right=30, dotted]
%     (m-1-2) edge node {\( \not \)} (m-1-1)
%     (m-2-2) edge node {\( \not \)} (m-2-1)
%     (m-1-4) edge node {\( \not \)} (m-1-3)
%     (m-2-4) edge node {\( \not \)} (m-2-3);
%   \path[>=latex,->,bend right=30, dotted]
%     (m-1-3) edge node {\( ? \)} (m-1-2)
%     (m-2-3) edge node {\( ? \)} (m-2-2);
% \end{tikzpicture}
\end{center}
\caption{Diagram of covering properties related to the Menger game}
\label{menSpec}
\end{figure}

>>>>

\usepackage{tikz}
\usetikzlibrary{matrix}

@@

\keywords{Menger's property, Menger's game, limited information strategies}

@@

It will be convenient to consider subsets of \(X\) rather than subsets of
the open covers.

\begin{definition}
  For each cover \(\mc U\) of \(X\), \(S\subseteq X\) is
  \term{\(\mc U\)-finite} if
  there exists a finite subcollection of \(\mc U\) which covers \(S\).
\end{definition}

@@

\begin{proposition}
  A space \(X\) is Menger if and only if
  for every sequence \(\<\mc U_0,\mc U_1,\dots\>\)
  of open covers of \(X\) there exists a sequence
  \(\<F_0,F_1,\dots\>\) such that \(F_n\subseteq X\), \(F_n\) is
  \(\mc U_n\)-finite, and \(X=\bigcup_{n<\omega}F_n\).
\end{proposition}

This is the characterization we will use in this paper.
A game version of the Menger property is also often considered.

@@

As with the Menger property, authors usually characterize this game using
finite subsets \(\mc F_n\)
of \(\mc U_n\) instead (and often refer to it as \(G(\mc O,\mc O)\) as
with the selection property above).
This is obviously equivalent in the case of perfect
information, and is also equivalent
in the case of limited information, provided \(\pl F\)
knows \(\mc U_n\) during round \(n\). However, we make this change as we
will investigate \(0\)-Markov strategies which consider no moves of
the opponent, and instead rely only on the current round number.

This game may be used to characterize the Menger property.

\begin{definition}
  If \(\pl A\) has a winning strategy for a game \(G\) (which defeats every
  possible counterattack by her opponent), then we write \(\pl A\win G\).
\end{definition}

\begin{theorem}[Hurewicz \cite{MR1544773}]
  A space \(X\) is Menger if and only if \(\pl C\notwin\menGame{X}\).
\end{theorem}

\section{Limited information strategies}

Recall the following definitions.

\begin{definition}
  A \(k\)-tactical strategy for a game \(G\) with moveset \(M\) is a function
  \(\sigma:M^{\leq k}\to M\); intuitively, it is a strategy which only considers
  the previous \(k\) moves of the opponent. If a winning \(k\)-tactical strategy
  exists for \(\pl P\) in the game \(G\), then we write \(\pl P\ktactwin{k} G\).
\end{definition}

\begin{definition}
  A \(k\)-Markov strategy for a game \(G\) with moveset \(M\) is a function
  \(\sigma:M^{\leq k}\times\omega\to M\); intuitively, it is a strategy which
  only considers the previous \(k\) moves of the opponent and the round number.
  If a winning \(k\)-Markov strategy exists for
  \(\pl P\) in the game \(G\), then we write \(\pl P\kmarkwin{k} G\).
\end{definition}

We will call \(k\)-tactical strategies ``\(k\)-tactics'' and \(k\)-Markov strategies
``\(k\)-marks''. If the \(k\) is omitted then it is assumed that \(k=1\). In
addition, note that some authors refer to tactics as
\term{stationary strategies}.

Tactics will be of interest in a game discussed later; proving
the following is an easy exercise.

\begin{proposition}
  \(X\) is compact if and only if
  \(\pl F \tactwin \menGame{X}\) if and only if
  \(\pl F \ktactwin{k+1} \menGame{X}\) for some \(k<\omega\).
\end{proposition}

@@

\begin{proposition}
  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\); in fact,
  \(\oneptlind{\omega_1}\) is not \(\sigma\)-compact.
\end{proposition}

The greatest advantage of a strategy which has knowledge of two or more previous
moves of the opponent, versus only knowledge of the most recent move, is the
ability to react to changes from one round to the next. It's this ability to
react that will give \(\pl F\) her winning \(2\)-Markov strategy in the Menger
game on \(\oneptlind\omega_1\). This may be proven directly; however, we will
postpone giving a proof so that we may take advantage of an equivalent
game characterization of this property.

\section{Scheepers' filling games}

We now turn to a related game whose \(k\)-tactics were studied by Marion
Scheepers in \cite{MR1129143}.

\begin{game}
  Let \(\schFillStrictGame\kappa\) denote
  \term{Scheepers' strict union filling game}
  with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
  \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
  \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
  by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).

@@

In \(\menGame{\oneptlind\kappa}\), \(\pl C\) essentially chooses a countable set
to not include in her neighborhood of \(\infty\), followed by \(\pl F\) choosing
a finite subset of this complement to cover during each round. Thus,
\(\pl F\) need only be concerned with the \textit{intersection} of the
countable sets chosen by \(\pl C\) in \(\menGame{\oneptlind\kappa}\), rather
than the union as in \(\schFillStrictGame\kappa\).

Another difference between these games:
Scheepers required that \(\pl C\) always choose strictly
growing countable sets. If the goal is to study tactics,
then \(\pl C\) cannot be allowed to trap \(\pl F\) in a loop by
repeating the same
moves. But by eliminating this requirement, the study can then turn to Markov
strategies, bringing the game further in line with the Menger game played upon
\(\oneptlind\kappa\).

We introduce a few games to make the relationship between Scheeper's
\(\schFillStrictGame\kappa\) and \(\menGame{\oneptlind\kappa}\) more precise.

\begin{game}
  Let \(\schFillGame\kappa\) denote the
  \term{union filling game} which proceeds analogously
  to \(\schFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
  is reduced to \(C_{n+1}\supseteq C_n\).
\end{game}

\begin{game}
  Let \(\schFillInitialGame\kappa\) denote the
  \term{initial filling game} which proceeds analogously
  to \(\schFillGame\kappa\), except that \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq C_0\).
\end{game}

\begin{game}
  Let \(\schFillIntGame\kappa\) denote the
  \term{intersection filling game} which proceeds analogously
  to \(\schFillInitialGame\kappa\), except that \(\pl C\) may choose any
  \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\) wins whenever
  \(\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n\).
\end{game}

\begin{figure}[h]
\begin{center}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
  {
    \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa} &
    \pl F \kmarkwin{k+1}\schFillIntGame\kappa \\

    \pl F \kmarkwin{k+1}\schFillInitialGame\kappa &
    \pl F \kmarkwin{k+1}\schFillGame\kappa \\

    &
    \pl F \ktactwin{k+1}\schFillStrictGame\kappa \\
  };
  \path[>=latex,->]
    (m-1-1) edge (m-2-1)
    (m-1-2) edge (m-2-2)
    (m-3-2) edge (m-2-2);
  \path[>=latex,<->]
    (m-1-1) edge (m-1-2)
    (m-2-1) edge (m-2-2);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheepers/Menger game implications}
\label{fillingGamesDiagram}
\end{figure}

\begin{theorem}
For any cardinal \(\kappa\geq\omega\) and integer \(k<\omega\),
Figure \ref{fillingGamesDiagram} holds.
\end{theorem}

\begin{proof}
  \(\pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillIntGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\menGame{\oneptlind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
  countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
  into the open cover \([C]^1\cup\{\oneptlind\kappa\setminus C\}\)
  (resp. finite sequence of such open covers). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      C\cap\sigma(\mc U(s\concat\<C\>),n)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillIntGame\kappa\).

  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\schFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
  cover \(\mc U\) of \(\oneptlind\kappa\) (resp. finite sequence \(s\) of such covers)
  into a countable set \(C\) which is the complement of some neighborhood of
  \(\infty\) in \(\mc U\) (resp. finite sequence of such countable sets).
  Then \(\tau\) defined by
    \[
      \tau(s\concat\<\mc U\>,n)
        =
      (\oneptlind\kappa\setminus C(\mc U))
        \cup
      \sigma(C(s\concat\<\mc U)\>),n)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\oneptlind\kappa}\).

  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\schFillIntGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
  in \(\schFillInitialGame\kappa\).

  \(\pl F \kmarkwin{k+1}\schFillInitialGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillGame\kappa\): Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\schFillInitialGame\kappa\). For each finite sequence \(s\), let \(t\preceq s\) mean \(t\)
  is a final subsequence of \(s\). Then \(\tau\) defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      \bigcup_{t\preceq s, m\leq n}
      \sigma(t\concat\<C\>,m)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).

  \(\pl F \kmarkwin{k+1}\schFillGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
  \(\schFillGame\kappa\). \(\sigma\) is also a winning
  \((k+1)\)-mark for \(\pl F\)
  in \(\schFillInitialGame\kappa\).

  \(\pl F \ktactwin{k+1}\schFillStrictGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k+1}\schFillGame\kappa\):
  Let \(\sigma\) be a winning \(k\)-tactic for \(\pl F\) in
  \(\schFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
  be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
  Then \(\tau\) defined by
    \[
      \tau(\<C_0,\dots,C_i\>,n)
        =
      \sigma(\<C_0+(n-i),\dots,C_i+n\>)
    \]
  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).
\end{proof}

While we have not shown a direct implication between the Menger game and
Scheeper's original filling game, Scheepers introduced the statement
\(\alcompS\kappa\) relating to the almost-compatability of functions
from countable subsets of \(\kappa\) into \(\omega\) which may be applied to
both.

@@

Scheepers went on to show that \(\alcompS\kappa\) implies
\(\pl F \ktactwin2 \schFillStrictGame\kappa\). This proof, along with the following
facts, give us inspiration for
finding a winning \(2\)-Markov strategy in the Menger game played on
\(\oneptlind\kappa\).

@@

\begin{figure}[h]
\begin{center}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
  {
    &
    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
    \pl F \kmarkwin2\schFillIntGame\kappa \\

    \alcompS\kappa &
    \pl F \kmarkwin2\schFillInitialGame\kappa &
    \pl F \kmarkwin2\schFillGame\kappa \\

    &
    &
    \pl F \ktactwin2\schFillStrictGame\kappa \\
  };
  \path[>=latex,->]
    (m-2-1) edge (m-1-2)
    (m-2-1) edge (m-2-2)
    (m-2-1) edge (m-3-3)
    (m-1-2) edge (m-2-2)
    (m-1-3) edge (m-2-3)
    (m-3-3) edge (m-2-3);
  \path[>=latex,<->]
    (m-1-2) edge (m-1-3)
    (m-2-2) edge (m-2-3);
\end{tikzpicture}
\end{center}
\caption{Diagram of Filling/Menger game implications with \(\alcompS\kappa\)}
\label{fillingGamesDiagram2}
\end{figure}

@@

\begin{proof}
  Since \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\) was
  a main result of \cite{MR1129143}, it is sufficient to show that
  \(\alcompS\kappa\Rightarrow \pl F \kmarkwin2\schFillIntGame\kappa\).

@@

\begin{figure}[h]
\begin{center}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
  {
     \pl F \markwin \menGame{X} &
     \pl F \kmarkwin2 \menGame{X} &
     \pl F \win \menGame{X} &
     \pl C \notwin \menGame{X} \\

     \text{Markov Menger} &
     2\text{-Markov Menger} &
     \text{Perfect Menger} &
     \text{Menger} \\
  };
  \path[>=latex,<->]
    (m-1-1) edge (m-2-1)
    (m-1-2) edge (m-2-2)
    (m-1-3) edge (m-2-3)
    (m-1-4) edge (m-2-4);
  \path[>=latex,->]
    (m-1-1) edge (m-1-2)
    (m-2-1) edge (m-2-2)
    (m-1-2) edge (m-1-3)
    (m-2-2) edge (m-2-3)
    (m-1-3) edge (m-1-4)
    (m-2-3) edge (m-2-4);
  \path[>=latex,->,bend right=30, dotted]
    (m-1-2) edge node {\( \not \)} (m-1-1)
    (m-2-2) edge node {\( \not \)} (m-2-1)
    (m-1-4) edge node {\( \not \)} (m-1-3)
    (m-2-4) edge node {\( \not \)} (m-2-3);
  \path[>=latex,->,bend right=30, dotted]
    (m-1-3) edge node {\( ? \)} (m-1-2)
    (m-2-3) edge node {\( ? \)} (m-2-2);
\end{tikzpicture}
\end{center}
\caption{Diagram of covering properties related to the Menger game}
\label{menSpec}
\end{figure}
